Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/introduction.tex
minor typos in abstract and intro

\paragraph{3. Evaluating Witnesses}
%
Of course, the problem of finding witnesses is
undecidable. In fact, due to the necessarily
conservative nature of static typing, there
may not even exist any witnesses for a given
ill-typed program.
%
Thus, our approach is a heuristic that is only useful
if it can find \emph{compact} witnesses for
\emph{real-world} programs.
%
Our third contribution is an extensive evaluation of our approach
on two different sets of ill-typed programs obtained by instrumenting
compilers used in beginner's classes~(\S~\ref{sec:evaluation}).
%
The first is the \uwbench\ data set~\cite{lerner_searching_2007}
comprising \uwsize\ ill-typed programs.
%
The second is a new \ucsdbench\ data set, comprising \ucsdsize\
ill-typed programs.
%
We show that for both data sets, our technique is able to generate
witnesses for nearly 90\% of the programs, in under a second the
vast majority of cases.
%
Furthermore, we show that a simple interactive strategy yields
compact counterexample traces with fewer than 5 steps for 60\%
of the programs, and under 10 steps for 90\% of the programs.

>>>>

\paragraph{3. Evaluating Witnesses}
%
Of course, the problem of finding witnesses is
undecidable. In fact, due to the necessarily
conservative nature of static typing, there
may not even exist any witnesses for a given
ill-typed program.
%
Thus, our approach is a heuristic that is only useful
if it can find \emph{compact} witnesses for
\emph{real-world} programs.
%
Our third contribution is an extensive evaluation of our approach
on two different sets of ill-typed programs obtained by instrumenting
compilers used in beginner's classes~(\S~\ref{sec:evaluation}).
%
The first is the \uwbench\ data set~\cite{lerner_searching_2007}
comprising \uwsize\ ill-typed programs.
%
The second is a new \ucsdbench\ data set, comprising \ucsdsize\
ill-typed programs.
%
We show that for both data sets, our technique is able to generate
witnesses for nearly 90\% of the programs, in under a second in the
vast majority of cases.
%
Furthermore, we show that a simple interactive strategy yields
compact counterexample traces with fewer than 5 steps for 60\%
of the programs, and under 10 steps for 90\% of the programs.
